---
title: "Linear regression with a spline term"
subtitle: "Shiny App Pitch"
author: "Tejus"
date: "25/10/2020"
output: 
  beamer_presentation: default
  widescreen: yes
  smaller: yes
runtime: shiny
mode: 'selfcontained '
widescreen: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(shiny)
library(magick)
```

## Fitting a functions using linear models

* Consider a model $Y_i = f(X_i) + \epsilon$. 

* The `shiny app` demonstrates fitting such a model using linear models (called scatterplot smoothing)

* The model adds extra terms as below,
  $$
  Y_i = \beta_0 + \beta_1 X_i + \sum_{k=1}^d (x_i - \xi_k)_+ \gamma_k + \epsilon_{i}
  $$
where $(a)_+ = a$ if $a > 0$ and $0$ otherwise and $\xi_1 \leq ... \leq \xi_d$ are known knot points.

* Application allows the user to add & adjust 2 knot points and demonstrates how the $R^2$
improves & $\sigma$ is reduced.


## The linear model approximation !! 

- Almost always an approximation, and sometimes a poor one.

```{r echo=FALSE, fig.align='center', fig.width=6}
# Linear fit
fit1 <- lm(wt ~ disp, mtcars)
Caption1 <- paste("lm(wt ~ disp)\n","Residual standard error : ", round(summary(fit1)$sigma,4), "  R-square : ", round(summary(fit1)$r.squared,4), sep="" )

plot(mtcars$disp, mtcars$wt, pch = 16, xlab = "Displacement", ylab = "Weight)", main = Caption1  )
abline(fit1, lwd= 2, col="red")

```
- The app first shows the shortcomings when launched. 


## Interactive improvements suggested !! 

- User has the options to slide & set the 2 breaks points (green lines) to adjust $\sigma$ & $R^2$


```{r UI, echo=FALSE, fig.align='center',fig.height=4, fig.width=6}
x <- mtcars[order(mtcars$disp),]

# Knot terms
knots <- c(150, 350)
splineTerms1 <- sapply(knots, function(knot){ifelse(x$disp - knot > 0, (x$disp - knot)^2, 0) })

xMat <- cbind(Intercept = 1, Displacement = x$disp, splineTerms1 )
colnames(xMat) <- c( "Intercept", "Displacement", "Knot1", "Knot2")

# model fitting
fit1 <- lm(x$wt ~ disp, x)
fit2 <- lm(x$wt ~ xMat-1)
yhat <- predict(fit2)

Caption <- paste("lm(wt ~ disp -xMat - 1)\n","Residual standard error : ", round(summary(fit2)$sigma,4), "  R-square : ", round(summary(fit2)$r.squared,4), sep="" )


# Plotting
plot(mtcars$disp, mtcars$wt, pch = 16, xlab = "Displacement", ylab = "Weight", main = Caption )
abline(fit1, lwd= 2, col="red")
lines(x$disp, yhat, lwd = 2, col = "dodgerblue")
abline(v = knots, lwd = 2, col="green")

```

- **Note : ** for **`r Caption1`**


## Demo 

- Uncheck the `Hide spline checkbox` & get started !!

```{r fig.align="left", fig.height=6 ,fig.width= 6, echo=FALSE}

img <- image_read("./Code/Slide.png")
print(img)

```

## Detailed summary

- You can check for additional parameters and final coefficients in `Summary` tab

```{r fig.align="left", fig.height=6 ,fig.width= 6, echo=FALSE, warning=FALSE, fig.align="center"}

img2 <- image_read("./Code/Slide2.png")
print(img2)

```

## Link to the app (Hosted on Shiny Server)

- <https://the-eon-flux.shinyapps.io/Shiny_App_Pitch/?_ga=2.151732921.1645565962.1603605167-1419273587.1603605167>














