---
title: "World Religion Data"
author: "Tejus"
date: "25/10/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(reshape2)
library(plotly)

Df <- read.csv("./Code/WRP national data.csv", header = T)

ColI <- c(1,2,3,9,22,26,27,28)
FinalDf <- as.data.frame(Df[,ColI])


```


## Introduction

* This dataset provides information regarding the number of adherents by 
religion, as well as the percent of the state's population practicing a 
given religion, **observed at five-year intervals**. 

* Data for the following 4 countries is plotted here : 

      - India (IND)
      - United States of America (US)
      - Pakistan (PAK)
      - China (CHN)

## World Religion Project : Indian Data

```{r Religion, echo = FALSE}
# India Data
IND_Data <- subset(FinalDf, name == "IND")

colnames(IND_Data) <- c("Year", "State", "Country","Christians", "Muslims", "Buddhist", "Jains", "Hindus")
Ind_Melted <- melt(IND_Data, id = c("Year", "State", "Country"), measure.vars = c("Christians", "Muslims", "Buddhist", "Jains", "Hindus") )

# Plotting
g <- ggplot(Ind_Melted, aes(x = Year, y = value/10000 )) + geom_point(size = 2, aes(color=variable)) + labs(title = "Time Series of Indian Population Growth") + labs(x= "Year", y = "10K Population Count")
ggplotly(g)


```

* Hover over each point for more info at that point.

## World Religion Project : US data

```{r US_Data, echo=FALSE }
# US Data
US_Data <- subset(FinalDf, name == "USA")
colnames(US_Data) <- c("Year", "State", "Country","Christians", "Muslims", "Buddhist", "Jains", "Hindus")
US_Melted <- melt(US_Data, id = c("Year", "State", "Country"), measure.vars = c("Christians", "Muslims", "Buddhist", "Jains", "Hindus") )

# Plotting
g <- ggplot(US_Melted, aes(x = Year, y = value/10000)) + geom_point(size = 2, aes(color=variable)) + labs(title = "Time Series of US Population Growth") + labs(x= "Year", y = "10K Population Count")
ggplotly(g)


```


* Hover over each point for more info at that point.

## World Religion Project : Pakistan Data

```{r PAK, echo=FALSE}
# PAK Data
PAK_Data <- subset(FinalDf, name == "PAK")
colnames(PAK_Data) <- c("Year", "State", "Country","Christians", "Muslims", "Buddhist", "Jains", "Hindus")

PAK_Melted <- melt(PAK_Data, id = c("Year", "State", "Country"), measure.vars = c("Christians", "Muslims", "Buddhist", "Jains", "Hindus") )

# Plotting
g <- ggplot(PAK_Melted, aes(x = Year, y = value/10000)) + geom_point(size = 2, aes(color=variable)) + labs(title = "Time Series of PAK Population Growth") + labs(x= "Year", y = "10K Population Count")
ggplotly(g)


```

* Hover over each point for more info at that point.


## World Religion Project : China Data

```{r CHN, echo=FALSE}
# China Data
CHN_Data <- subset(FinalDf, name == "CHN")
colnames(CHN_Data) <- c("Year", "State", "Country","Christians", "Muslims", "Buddhist", "Jains", "Hindus")

CHN_Melted <- melt(CHN_Data, id = c("Year", "State", "Country"), measure.vars = c("Christians", "Muslims", "Buddhist", "Jains", "Hindus") )

# Plotting
g <- ggplot(CHN_Melted, aes(x = Year, y = value/10000)) + geom_point(size = 2, aes(color=variable)) + labs(title = "Time Series of CHN Population Growth") + labs(x= "Year", y = "10K Population Count")
ggplotly(g)


```

* Hover over each point for more info at that point.

## European Countries

```{r EU_Nations, eval=FALSE, echo=FALSE}

# All coutrny IDs
All_C <- read.csv("./Code/All.csv", header = TRUE)
Res <- subset(All_C, All_C$region == "Europe")[1:3]
dim(Res)

colnames(Res) <- c("Country", "2Ltr_Code", "name")

Mer <- merge(FinalDf, Res, by="name", all.x = FALSE)
Mer <- Mer[, -c(3,6,7,9,10)]
colnames(Mer) <- c("name", "Year", "Christians", "Muslims", "Hindus")

Mer <- melt(Mer, id = c("name", "Year"), measure.vars = c("Christians", "Muslims", "Hindus") )
EU_Nations <- unique(Mer$name)


pdf("EU_Population_Growth.pdf")
sapply(EU_Nations, function(Nation){
    Title = paste("Time Series vs Population Growth for :", Nation, sep = " ")
    g <- ggplot(Mer[Mer$name == Nation,], aes(x = Year, y = value/10000)) + geom_point(size = 2, aes(color=variable)) + labs(title = Title) + labs(x= "Year", y = "10K Population Count") 
    plot(g)
})

dev.off()

g <- ggplot(Mer, aes(x = Year, y = value/10000)) + geom_point(size = 2, aes(color=variable)) + labs(title = "Time Series of EU Nations Population Growth") + labs(x= "Year", y = "10K Population Count") + facet_grid(name~.)
g
#ggplotly(g)

```

## Sources & References

- Data was obtained from <https://data.world/cow/world-religion-data>

- All the credit for data goes to : 

  - Zeev Maoz and Errol A. Henderson. 2013. The World Religion Dataset, 
      1945-2010: Logic, Estimates, and Trends in International Interactions, 
      39: 265-291.
      











